Adaptive group-regularized logistic elastic net regression

### 2019-02-11 docs/manuscript.Rnw
commit before pull

\documentclass[a4paper,hidelinks]{article}
\usepackage{url,bm,algorithm,algpseudocode,bbm,bm,amsmath,amssymb,amsthm,amsfonts,graphics,graphicx,epsfig,rotating,caption,subcaption,natbib,appendix,titlesec,multicol,hyperref,verbatim,bbm,algorithm,algpseudocode,threeparttable, booktabs,dsfont,parskip}

>>>>

\documentclass[a4paper,hidelinks]{article}
\usepackage{url,bm,algorithm,algpseudocode,bbm,amsmath,amssymb,amsthm,
amsfonts,graphics,graphicx,epsfig,rotating,caption,subcaption,natbib,appendix,
titlesec,multicol,hyperref,verbatim,threeparttable,booktabs,dsfont,parskip}
